\documentclass{article}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage[dvips]{graphicx}
\usepackage{ifthen}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{upgreek}
\usepackage{listings}
\usepackage[left=0.75in, top=1in, right=0.75in, bottom=1in]{geometry}

\lstloadlanguages{Python}
\lstset{language=Python,
        frame=single,
       }

% Homework Specific Information
\newcommand{\hmwkTitle}{Assignment 3}
\newcommand{\hmwkSubTitle}{}
\newcommand{\hmwkDueDate}{12 October 2012}
\newcommand{\hmwkClass}{CS 640}
\newcommand{\hmwkClassTime}{2:20}
\newcommand{\hmwkClassInstructor}{Dr Ranganath}
\newcommand{\hmwkAuthorName}{Ted Satcher}

\pagestyle{fancy}
\lhead{\hmwkAuthorName}
\chead{\hmwkClass\ (\hmwkClassInstructor\ \hmwkClassTime): \hmwkTitle}
\rhead{\firstxmark}
\lfoot{\lastxmark}
\cfoot{}
\rfoot{Page\ \thepage\ of\ \protect\pageref{LastPage}}
\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\title{\vspace{2in}\textmd{\textbf{\hmwkClass:\ \hmwkTitle\ifthenelse{\equal{\hmwkSubTitle}{}}{}{\\\hmwkSubTitle}}}\\\normalsize\vspace{0.1in}\small{Due\ on\ \hmwkDueDate}\\\vspace{0.1in}\large{\textit{\hmwkClassInstructor\ \hmwkClassTime}}\vspace{3in}}
\date{}
\author{\textbf{\hmwkAuthorName}}

\begin{document}
\maketitle

\section{NOTES}
- Starting work on the neural net.

- Coming to the conclusion that a big part of neural network
design is how to set up the data and get access to it.

- My choice in this assignment was to restrict the problem to a
three layer network, input, hidden and output, but to not
otherwise restrict it.  That is, I wanted the ability to add
an arbitray number of input, hidded and output nodes.  I also
wanted the flexibility to swap out the squashing function.

- The primary data structure for my network is in the DataTable
class in the data_table module.  The DataTable class is the central
element of my architecture.  Its primary purpose is to provide
access to the data elements representing the network to clients
which are primarily the nodes in the network.

\end{document}